Appendix S1

### 2020-06-18 analysis/paper/appendix/appendix_s1.Rmd
moved appendix to it's own folder. added a _bookdown.yml file to make the figure and table numbering correct for the appendix.

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@biomark.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@biomark.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richie.Carmichael@biomark.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@biomark.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@biomark.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
      includes:
        in_header: ../templates/header_appendixS.tex
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/appendix/",
  dpi = 600,
  appendix = TRUE
)
```

@@

# options for table formating with "kable()"
options(knitr.kable.NA = '-')
options(knitr.table.format = "pandoc")

@@

```{r load-data}
fish_hab = read_rds("../data/derived_data/fish_hab.rds")
hab_dict = read_rds("../data/derived_data/hab_dict.rds")
sel_hab_mets = read_rds("../data/derived_data/sel_hab_mets.rds")
hab_data = read_rds("../data/derived_data/hab_data.rds")
```

@@

@@

```{r mic-tab}
mine_tab_df = mine_res %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  filter(MetricCategory != 'Land Classification') %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC,
         `Percent Missing` = perc_NA,
         `Percent 0-value`,
         selected)

mine_tab_df %>%
  select(-selected) %>%
  kable(digits = 3,
        format = 'html',
        # format = 'latex',
        booktabs = T,
        caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.') %>%
  kable_styling(fixed_thead = T) %>%
  row_spec(row = which(mine_tab_df$selected),
           bold = T)

@@

```{r mine-facet-fig, fig.cap = 'Barplots of MIC statistics, faceted by habitat category.'}
mine_res %>%
  filter(MetricCategory != 'Land Classification') %>%
  mutate(MetricCategory = recode(MetricCategory,
                                 'ChannelUnit' = 'Channel\nUnit',
                                 'SideChannel' = 'Side\nChannel',
                                 'WaterQuality' = 'Water\nQuality')) %>%
  ggplot(aes(x = Name,
             y = MIC)) +
  geom_col(fill = 'blue') +
  coord_flip() +
  facet_wrap(~ MetricCategory,
             scales = 'free_y',
             ncol = 3) +
  theme(legend.position = 'bottom',
        axis.text = element_text(size = 5))
```

@@

```{r corr-fig, results='hide', fig.width = 5, fig.height = 5, fig.show = "hold", fig.cap = "Correlation plots of metrics, faceted by habitat category."}
cor_plot_df = tibble(Category = names(hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]),
                     cor_mat = hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]) %>%
  mutate(cor_plot = map2(cor_mat,
                         Category,
                         .f = function(x, y) {
                           ggcorrplot::ggcorrplot(x,
                                                  method = 'circle',
                                                  hc.order = T,
                                                  type = 'lower',
                                                  title = y,
                                                  colors = c('blue4', 'white', 'red3'))
                         }))

>>>>

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@biomark.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@biomark.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richie.Carmichael@biomark.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@biomark.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@biomark.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks2.lua
      - --lua-filter=../../templates/pagebreak.lua
      includes:
        in_header: ../../templates/header_appendixS.tex
bibliography:
- ../references.bib
- ../packages.bib
csl: "../../templates/ecological-applications.csl" # Insert path for the bib-style
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../../figures/appendix/",
  dpi = 600,
  appendix = TRUE
)
```

@@

# options for table formating with "kable()"
options(knitr.kable.NA = '-')
# options(knitr.table.format = "pandoc")

@@

```{r load-data}
fish_hab = read_rds("../../data/derived_data/fish_hab.rds")
hab_dict = read_rds("../../data/derived_data/hab_dict.rds")
sel_hab_mets = read_rds("../../data/derived_data/sel_hab_mets.rds")
hab_data = read_rds("../../data/derived_data/hab_data.rds")
```

@@

# remove Land Classification metrics
poss_hab_mets <- poss_hab_mets %>%
  filter(MetricCategory != 'Land Classification')

@@

```{r mic-tab}
mine_tab_df = mine_res %>%
  mutate(`Percent 0-value` = 1 - perc_non0) %>%
  group_by(MetricCategory) %>%
  slice(1:10) %>%
  select(Category = MetricCategory,
         Name,
         Abbrv = Metric,
         MIC,
         `Percent Missing` = perc_NA,
         `Percent 0-value`,
         selected)

mine_tab_df %>%
  select(-selected) %>%
  kable(digits = 3,
        # format = 'html',
        # format = 'latex',
        booktabs = T,
        longtable = T,
        caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.') %>%
  kable_styling(fixed_thead = T,
                latex_options = c('repeat_header',
                                  'scale_down',
                                  'HOLD_position')) %>%
  row_spec(row = which(mine_tab_df$selected),
           bold = T) %>%
  column_spec(2, width = "2in") %>%
  column_spec(3, width = "1in") %>%
  column_spec(c(4:6), width = "0.5in")

@@

```{r mine-facet-fig, fig.cap = 'Barplots of MIC statistics, faceted by habitat category.'}
mine_res %>%
  mutate(MetricCategory = recode(MetricCategory,
                                 'ChannelUnit' = 'Channel\nUnit',
                                 'SideChannel' = 'Side\nChannel',
                                 'WaterQuality' = 'Water\nQuality')) %>%
  ggplot(aes(x = Name,
             y = MIC)) +
  geom_col(fill = 'blue') +
  coord_flip() +
  facet_wrap(~ MetricCategory,
             scales = 'free_y',
             ncol = 2) +
  theme(legend.position = 'bottom',
        axis.text = element_text(size = 5))
```

@@

```{r corr-fig, eval = T, results='hide', out.width = "90%", fig.show = "hold", fig.cap = "Correlation plots of metrics, faceted by habitat category. Larger circles correspond to larger correlation coefficients. The colors correspond to the correlation coefficient as well, and range from blue (-1) to white (0) to red (1)."}
cor_plot_df = tibble(Category = names(hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]),
                     cor_mat = hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]) %>%
  mutate(cor_plot = map2(cor_mat,
                         Category,
                         .f = function(x, y) {
                           ggcorrplot::ggcorrplot(x,
                                                  method = 'circle',
                                                  hc.order = T,
                                                  type = 'lower',
                                                  title = y,
                                                  colors = c('blue4', 'white', 'red3'))
                         }))

cor_plot_df$cor_plot

```{r corr-fig2, eval = F, out.width = "50%", fig.cap = "Correlation plots of metrics, faceted by habitat category. Larger circles correspond to larger correlation coefficients. The colors correspond to the correlation coefficient as well, and range from blue (-1) to white (0) to red (1)."}
cor_plot_df = tibble(Category = names(hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]),
                     cor_mat = hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]) %>%
  mutate(cor_plot = map2(cor_mat,
                         Category,
                         .f = function(x, y) {
                           corrplot::corrplot.mixed(x,
                                                    upper = 'ellipse',
                                                    tl.pos = 'lt',
                                                    order = 'FPC')
                         }))

### 2020-06-18 analysis/paper/appendix_s1.Rmd
moved appendix to it's own folder. added a _bookdown.yml file to make the figure and table numbering correct for the appendix.

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@biomark.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@biomark.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richie.Carmichael@biomark.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@biomark.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@biomark.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
      includes:
        in_header: ../templates/header_appendixS.tex
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
---

@@

mine_tab_df %>%
  select(-selected) %>%
  kable(digits = 3,
        format = 'html',
        # format = 'latex',
        booktabs = T,
        caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.') %>%
  kable_styling(fixed_thead = T) %>%
  row_spec(row = which(mine_tab_df$selected),
           bold = T)

@@

```{r mine-facet-fig, fig.cap = 'Barplots of MIC statistics, faceted by habitat category.'}
mine_res %>%
  filter(MetricCategory != 'Land Classification') %>%
  mutate(MetricCategory = recode(MetricCategory,
                                 'ChannelUnit' = 'Channel\nUnit',
                                 'SideChannel' = 'Side\nChannel',
                                 'WaterQuality' = 'Water\nQuality')) %>%
  ggplot(aes(x = Name,
             y = MIC)) +
  geom_col(fill = 'blue') +
  coord_flip() +
  facet_wrap(~ MetricCategory,
             scales = 'free_y',
             ncol = 3) +
  theme(legend.position = 'bottom',
        axis.text = element_text(size = 5))
```

@@

```{r corr-fig, results='hide', fig.width = 5, fig.height = 5, fig.show = "hold", fig.cap = "Correlation plots of metrics, faceted by habitat category."}
cor_plot_df = tibble(Category = names(hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]),
                     cor_mat = hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]) %>%
  mutate(cor_plot = map2(cor_mat,
                         Category,
                         .f = function(x, y) {
                           ggcorrplot::ggcorrplot(x,
                                                  method = 'circle',
                                                  hc.order = T,
                                                  type = 'lower',
                                                  title = y,
                                                  colors = c('blue4', 'white', 'red3'))
                         }))

>>>>

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@biomark.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@biomark.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richie.Carmichael@biomark.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@biomark.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@biomark.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
      includes:
        in_header: ../templates/header_appendixS.tex
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography:
- references.bib
- packages.bib
csl: "../templates/ecological-applications.csl" # Insert path for the bib-style
---

@@

mine_tab_df %>%
  select(-selected) %>%
  kable(digits = 3,
        # format = 'html',
        # format = 'latex',
        booktabs = T,
        longtable = T,
        caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.') %>%
  kable_styling(fixed_thead = T,
                latex_options = c('repeat_header',
                                  'scale_down',
                                  'HOLD_position')) %>%
  row_spec(row = which(mine_tab_df$selected),
           bold = T) %>%
  column_spec(2, width = "2in") %>%
  column_spec(3, width = "1in") %>%
  column_spec(c(4:6), width = "0.5in")

@@

```{r mine-facet-fig, fig.cap = 'Barplots of MIC statistics, faceted by habitat category.'}
mine_res %>%
  filter(MetricCategory != 'Land Classification') %>%
  mutate(MetricCategory = recode(MetricCategory,
                                 'ChannelUnit' = 'Channel\nUnit',
                                 'SideChannel' = 'Side\nChannel',
                                 'WaterQuality' = 'Water\nQuality')) %>%
  ggplot(aes(x = Name,
             y = MIC)) +
  geom_col(fill = 'blue') +
  coord_flip() +
  facet_wrap(~ MetricCategory,
             scales = 'free_y',
             ncol = 2) +
  theme(legend.position = 'bottom',
        axis.text = element_text(size = 5))
```

@@

```{r corr-fig, eval = T, results='hide', out.width = "50%", fig.show = "hold", fig.cap = "Correlation plots of metrics, faceted by habitat category. Larger circles correspond to larger correlation coefficients. The colors correspond to the correlation coefficient as well, and range from blue (-1) to white (0) to red (1)."}
cor_plot_df = tibble(Category = names(hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]),
                     cor_mat = hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]) %>%
  mutate(cor_plot = map2(cor_mat,
                         Category,
                         .f = function(x, y) {
                           ggcorrplot::ggcorrplot(x,
                                                  method = 'circle',
                                                  hc.order = T,
                                                  type = 'lower',
                                                  title = y,
                                                  colors = c('blue4', 'white', 'red3'))
                         }))

# for(i in 1:nrow(cor_plot_df)) {
#   print(cor_plot_df$cor_plot[i])
# }
cor_plot_df$cor_plot

# cowplot::plot_grid(plotlist = cor_plot_df$cor_plot,
#                    ncol = 2)

```{r corr-fig2, eval = F, out.width = "50%", fig.cap = "Correlation plots of metrics, faceted by habitat category. Larger circles correspond to larger correlation coefficients. The colors correspond to the correlation coefficient as well, and range from blue (-1) to white (0) to red (1)."}
cor_plot_df = tibble(Category = names(hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]),
                     cor_mat = hab_corr$catg_cor[[1]][!sapply(hab_corr$catg_cor[[1]], is.null)]) %>%
  mutate(cor_plot = map2(cor_mat,
                         Category,
                         .f = function(x, y) {
                           corrplot::corrplot.mixed(x,
                                                    upper = 'ellipse',
                                                    tl.pos = 'lt',
                                                    order = 'FPC')
                         }))
